---
title: "{{< var md-05.title >}}"
subtitle: "{{< var course.long-title >}}"
author: "Lars Schöbitz"
date: "2026-06-04"
date-format: long
footer: "[{{< fa link >}} {{< var course.site-short >}}]({{< var course.site >}})"
logo: "../images/ghe-square-logo-vector.svg"
format:
  revealjs:
    theme: ../style/slides.scss
    transition: fade
    slide-number: true
    chalkboard: true
editor: source
execute:
  freeze: auto
  echo: true
---

# Publishing {background-color="#4C326A"}

## Quarto Pub

-   [Quarto Pub](https://quartopub.com/) is a free publishing service for content created with Quarto. It is ideal for blogs, course or project websites, books, presentations, and personal hobby sites.

-   Publish with `quarto publish`:

``` {.bash filename="Terminal"}
quarto publish quarto-pub
```

-   Gain a `_publish.yml` that is safe to check into version control.

## Our turn

::: task
Let's now publish our website to Quarto Pub.

-   Open your website project on Posit Cloud
-   In the Terminal, run `quarto publish quarto-pub`
-   Follow the authorisation prompts in the browser
:::

```{r}
#| echo: false
countdown::countdown(5)
```

## Other venues

For when you outgrow Quarto Pub:

-   GitHub Pages, Posit Connect, Netlify, Confluence, and more.
-   Full list: [quarto.org/docs/publishing](https://quarto.org/docs/publishing/)

# Wrap up {background-color="#4C326A"}

## Questions?

::: {.hand-purple-large style="text-align: center;"}
Anything about publishing you'd like clarified?
:::

```{r}
#| echo: false
countdown::countdown(2)
```

## Learn more

::: learn-more
[quarto.org/docs/publishing](https://quarto.org/docs/publishing/)

```{=html}
<iframe src="https://quarto.org/docs/publishing/" width="100%" height="500" style="border:2px solid #123233;" title="Quarto Journal Articles"></iframe>
```
:::

